Outline flowCore paper

### 2008-02-04 paper/outline.tex
git-svn-id: https://hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/flowCore@29821 bc3139a8-67e5-0310-9ffc-ced21a209358

\documentclass[12pt]{article}
\usepackage{url}

@@

R is a solid statistical framework/environment, particularly geared
towards the analysis the large numeric datasets like those arising
from high throughput experiments such as FC-HCS. Indeed, this open
source software already offers a wide range of statistical and
visualization methods developed for various field of application, many
of them relavant also to FC-HCS data analysis. In addition, R is a
research platform which bioinformaticians, computer scientists, and
statisticians are using to develop new tools for statistical data
analyis. For biological application, the Bioconductor project has
become the standard toolset...

@@

{\bf NLM:} should we mention prada and rflowcyt?

{\bf FH:} Maybe not, I think it is time to move away from history and
establish flowCore as the one software for flow in Bioconductor.

{\bf RB:} Since rflowcyt laid the groundwork for this work we might consider
inviting Tony Rossini to contribute to the manuscript, in which case we
wouldn't need to mention rflowcyt. It would be important to highlight
the differences between flowCore and commercial software packages,
including in philosophy (open vs. closed source) and interaction
(programmatic data analysis vs. GUI-driven).

@@

\end{document}

>>>>

\documentclass[12pt]{article}
\usepackage{url}
\usepackage[authoryear,round]{natbib}

@@

R is a solid statistical framework/environment, particularly geared
towards the analysis the large numeric datasets like those arising
from high throughput experiments such as FC-HCS. Indeed, this open
source software already offers a wide range of statistical and
visualization methods developed for various field of application, many
of them relevant also to FC-HCS data analysis. 
%% FIXME: either cite some of our paper or drop this sentence. 
%% I think it it too redundant with the one above it.
In addition, R is a research platform which
bioinformaticians, computer scientists, and statisticians are using to
develop new tools for statistical data analyis. For biological
application, the Bioconductor project has become the standard toolset
\citep{gentleman2006bos}...

NLM: reference to microarray ?
\textit{end--- example text}

@@

{\bf RB:}  It would be important to highlight
the differences between flowCore and commercial software packages,
including in philosophy (open vs. closed source) and interaction
(programmatic data analysis vs. GUI-driven).

@@

\bibliographystyle{plainnat}  
\bibliography{flowCoreRef} 
\end{document}
